---
title: "Assignment 1"
subtitle: "STATS 220 Semester One 2022"
author: "Thomas Jacobson (tjac776)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magick)

```

## Github Repository Information
Below is a link too my Github page where I share all of the projects I am working on/ Have worked on previously.

https://github.com/ThomasJ09/stats220

## Animated Gif Creation

```
```{r circle set up}
#These lines of code gather a red, orange and green circle for me too use later on in my code.

red_circle <- image_read("https://webstockreview.net/images/dot-clipart-2d-shape-5.png") %>%
  image_scale(700)

orange_circle <- image_read("https://www.publicdomainpictures.net/pictures/310000/nahled/orange-circle.png") %>%
  image_scale(700)

green_circle <- image_read("https://www.clipartkey.com/mpngs/m/306-3061708_green-circle-shape-clipart.png") %>%
  image_scale(700)
```

```{r frames}
# Here I create each frame using the circles I had previously gathered.

frame1 <- red_circle %>%
  image_annotate(text = "Touch", size = 100, gravity = "center") %>%
  image_scale(200) %>%
  image_extent("500x500")

frame2 <- orange_circle %>%
  image_annotate(text = "Pause", size = 100, gravity = "center") %>%
  image_scale(300) %>%
  image_extent("500x500")

frame3 <- green_circle %>%
  image_annotate(text = "Engage", size = 100, gravity = "center") %>%
  image_scale(500) %>%
  image_extent("500x500")

frame4 <- image_read("https://i.pinimg.com/originals/5d/fe/01/5dfe01065696d4939efcd5983fba95cf.jpg") %>% image_scale(500)
```

```{r animation}
# The first line of code puts all the frames together and the second line animates them.

frames <- c(frame1, frame2, frame3, frame4)

image_animate(frames, fps = 2)
```
```

## Learning Reflection

In module one the main thing I have learnt and will be taking away with me is how important it is too type code exactly how it is meant too be otherwise it will not work. For example if I was too name a function circle and then try use it again later in my code but use Circle or cricle instead of circle then my code will not work. I also learnt that it is important too put speech marks in certain places otherwise code will not work in the intended way. Learning how important it is too double check my code constantly will definitely make me a better programmer.


I am curious too learn more about how I could make a database, with lots of information that I can use too find things out about the population I ask.
